Beam-Helicity and Beam-Charge Asymmetries\\ \red{Arising From} the DVCS and Bethe--Heitler \\ Processes \red{Using} a Proton Target \underline{Paper Tag: PDVCS0607 (v2.4)} \underline{Drafting Committee: DC90 (\today)}

### 2012-01-25 results_dual.tex
Finished textual and figure changes

The curves in  figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the average value of the kinematic bins used for the data analysis. The solid and dashed curves show results of calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Lab., and the collider experiments at H{\sc era}. The basic model~\cite{Mue05,Kum07,Kum08} is a \red{flexible GPD representation that is based on both a Mellin-Barnes integral and dispersion integral representation with weakly entangled skewedness and $t$ dependences}. The solid curves represent the model fit without data from experiments \cite{Cam06} at Hall A of Jefferson Lab.; the model fit represented by the dashed curves includes these data. Both fits include the 1996-2005 H{\sc ermes} data. The model incorporates only twist-2 GPDs and so can provide results only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes. All of the relevant amplitudes reported here are well described by the model.

>>>>

The curves in  figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the average value of the kinematic bins used for the data analysis. The solid and dashed curves show results of calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Lab., and the collider experiments at H{\sc era}. The basic model~\cite{Mue05,Kum07,Kum08} is a \red{flexible GPD representation that is based on both a Mellin-Barnes integral and dispersion integral representation with weakly entangled skewedness and $t$ dependences}. The solid curves represent the model fit without data from experiments \cite{Cam06} at Hall A of Jefferson Lab.; the model fit represented by the dashed curves includes 1these data. Both fits include the 1996-2005 H{\sc ermes} data. The model incorporates only twist-2 GPDs and so can provide results only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes. All of the relevant amplitudes reported here are well described by the model.

### 2012-01-25 theory.tex
Finished textual and figure changes

\section{Introduction}
Generalised Parton Distributions (GPDs)
\cite{Mue94,Ji97,Rad97} encompass the familiar Parton
Distribution Functions (PDFs) and nucleon Form Factors (FFs) to provide a
comprehensive description of the structure of the nucleon. A thorough
description of the nucleon in terms of GPDs would allow the deduction
of the total angular momentum of partons in the nucleon, and the
construction of a longitudinal-momentum-dissected transverse spatial map of parton densities~\cite{Bur00}. The GPDs appear in experimental measurements in the form of complex-valued Compton Form Factors (CFFs), which are flavour-sums of convolutions of GPDs with hard scattering kernels. Constraints on these CFFs, and thus GPDs, can be obtained from measurements of exclusive \red{leptoproduction} processes. In particular, the exclusive leptoproduction of \red{a single} real photon from a nucleon or nucleus \red{that remains intact} ($e\,N\,\rightarrow\,e\,N\,\gamma$; see figure~\ref{spin}) is the simplest to describe and is the most widely-used reaction channel for such work (see \cite{Air01,Air06,Air08,Air09,Air10,Air10a,Air10b,Air11,Air11a}).

>>>>

\section{Introduction}
Generalised Parton Distributions (GPDs)
\cite{Mue94,Ji97,Rad97} encompass the familiar Parton
Distribution Functions (PDFs) and nucleon Form Factors (FFs) to provide a
comprehensive description of the structure of the nucleon. A thorough
description of the nucleon in terms of GPDs would allow the deduction
of the total angular momentum of partons in the nucleon, and the
construction of a longitudinal-momentum-dissected transverse spatial map of parton densities~\cite{Bur00}. The GPDs appear in experimental measurements in the form of complex-valued Compton Form Factors (CFFs), which are flavour-sums of convolutions of GPDs with hard scattering kernels. Constraints on these CFFs, and thus GPDs, can be obtained from measurements of exclusive \red{leptoproduction} processes. In particular, the exclusive leptoproduction of \red{a single} real photon from a nucleon or nucleus \red{that remains intact} ($e\,N\,\rightarrow\,e\,N\,\gamma$; see figure~\ref{spin}) is the simplest to describe and is the most widely-used reaction channel for such work (see \cite{Air01,Air06,Air08,Air09,Air10,Air10a,Air10b,Air11,Air11a,h101,h105,h107,h109,zeu03,zeu08,Maz07,Cam06,Ste01,Che06,Gir08,Gav09,Com10}).
